Probabilistic Forecasts in Hierarchical~Time~Series

### 2018-03-03 ProbabilisticCoherence.tex
Did some changes according to Tas's comments

Many research applications often involve a large collection of multiple time series some of which are aggregates of others.
These collections of time series are called hierarchical time series. For example, electricity demand of a country can be disaggregated along a geographical hierarchy. One would be interested in forecasting electricity demand of the whole country along with the demand of states, cities, and households. This is referred to as hierarchical forecasting. An important aspect of hierarchical forecasting is to have coherent forecasts across the hierarchy; that is, forecasts at lower levels should add up to their respective upper levels of aggregation.

There is a rich literature on producing coherent point forecasts in hierarchical time series. The traditional approaches involve bottom-up, top-down and middle-out methods. In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.
In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions of observed data \citep{Gross1990}.
Many studies in the literature have broadly discussed the relative advantages and disadvantages of bottom-up and top-down methods and situations in which they would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method. Apparently, these three approaches use only a part of the information available when producing coherent forecasts. This might result in inaccurate forecasts. For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.

As an alternative to these conventional methods, \citet{Hyndman2011} propose to use information from all the levels of the hierarchy and reconcile them to obtain coherent point forecasts. In this approach, independent forecasts of all series are initially obtained. It is very unlikely that these forecasts are coherent. Then, these forecasts are optimally combined through a regression model to obtain coherent forecasts. This study has given a rise to the concept of point forecast reconciliation in hierarchical time series. In general, any forecasting method that uses a set of incoherent forecasts and revises them to obtain coherent forecasts is referred to as forecast reconciliation method. Thus it is important to notice that bottom-up, top-down and middle-out methods are not reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.

In a recent study on point forecast reconciliation, \citet{Wickramasuriya2017} propose to minimize the trace of mean squared coherent forecasts errors to optimally reconcile a set of unbiased, incoherent forecasts. Assuring the resulting reconciled forecasts are unbiased, they found a unique analytical solution to the proposed minimization problem. They referred this to as MinT approach. This solution was further improved to be computationally feasible for high dimensional hierarchies.

In recent forecasting literature, it is being the rationality to provide the associated uncertainty about the future, in addition to the point forecasts. This is referred to as probabilistic forecasts \citep{Gneiting2014}. For example, \citet{McSharry2005} produced probabilistic forecasts in application to electricity demand, \citet{BenTaieb2017} in application to smart meter data, \citet{Pinson2009} in application to wind power generation, \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} in application to prediction of weather quantities.

Although there is a thorough literature on producing coherent point forecasts of hierarchical time series, a very limited attention has been given in the context of probabilistic forecasts. Recently \citet{BenTaieb2017} proposed an algorithm to produce coherent probabilistic forecasts with the application to UK electricity smart meter data. This is the only study that copes with the probabilistic forecasts in hierarchical time series thus far. In their approach, a sample from the mean reconciled predictive distribution of the bottom level will be first generated. This sample will be then aggregated to obtain the coherent probabilistic forecasts of the respective upper levels of the hierarchy. Hence this method is a bottom-up based approach. They further use MinT approach for the mean reconciliation of the bottom level predictive distribution and a copula based approach to model the dependency structure of the hierarchy, when producing the sample of bottom level probabilistic forecasts.

Our contribution in this paper is to provide a proper theoretical background for the probabilistic hierarchical forecasts. First, we redefine the coherency of point forecasts and the reconciliation of a set of incoherent point forecasts by using the concepts on vector spaces and measure theory. This will leads us to provide a proper definition for probabilistic forecast reconciliation. Due to the aggregation structure in the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate. We discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation and also in the evaluation of their predictive performances. Further, we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework.

Rest of the paper is structured as follows. We start with introducing the notations in Section \ref{sec:notation}. In Section \ref{sec:definitions} we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in Section \ref{sec:reconciliation}. Section \ref{sec:evaluation} discusses the methods that can be used for evaluation of probabilistic hierarchical forecasts. Section \ref{sec:gaussian} consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in the Gaussian framework and we enclose with the remarkable conclusions in Section \ref{sec:conclusions}.

@@

We first introduce notations where possible following \citet{Wickramasuriya2017}. Suppose $\bm{y}_t \in \mathbb{R}^n$ comprising all observations of the whole hierarchy at time $t$ and $\bm{b}_t \in \mathbb{R}^m$ comprising only the bottom level observations at  time $t$. Then due to the aggregation nature of the hierarchy we have,
\begin{equation}
  \bm{y}_t = \bm{Sb}_t,
\end{equation}
where $\bm{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold. Since this linear subspace is equivalent to the column space of $\bm{S}$, we denote it as $\mathscr{C}(\bm{S})$. Further the null space of $\bm{S}$ which is orthogonal to this linear subspace is denoted by $\mathscr{N}(\bm{S})$.

To understand the notations clearly, consider the hierarchy given in Figure 1.
\begin{figure}[H]
  \begin{center}
    \leaf{AA} \leaf{AB}
    \branch{2}{A}
    \leaf{BA} \leaf{BB}
    \branch{2}{B}
    \branch{2}{Tot}
    \qobitree
  \end{center}
  \caption{Two level hierarchical diagram}
\end{figure}

In any hierarchy, the most aggregated level is termed as level 0, the second most aggregated level is termed as level 1 and so on. This example consists of two levels. At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2. Then
$\bm{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$,
$\bm{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and
$$
  \bm{S} =
  \begin{pmatrix}
    1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &
  \end{pmatrix},
$$
where $I_4$ is a $4$-dimension identity matrix.

@@

The main purpose of this section is to provide formal definitions for coherent forecasts. We start with redefining the coherent point forecasts using the properties of vector spaces which is then followed by the definition of coherent probabilistic forecasts.

\begin{definition}[Coherent Point Forecasts]
Suppose $\breve{\bm{y}}_{t+h} \in \mathbb{R}^n$ consists point forecasts of each series in the hierarchy at time $t+h$.  $\breve{\bm{y}}_{t+h}$ is said to be \textit{Coherent} if it lies in a $m$-dimensional subspace of $\mathbb{R}^n$ which is spanned by the columns of $\bm{S}$.
\end{definition}

\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
Let $(\mathbb{R}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability measure space where $\mathscr{F}^m$ is a sigma algebra on $\mathbb{R}^m$. $\breve{\nu}(.)$ on the measurable space $(\mathscr{C}(\bm{S}), \mathscr{F}_{\bm{S}})$ is said to be coherent probability measure iff
$$
  \breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,
$$
where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$.
\end{definition}

@@

      \node at (0,5) {$\mathbb{R}^m$(domain of $\bm{S}$)};
      \node at (4,5) {$\mathbb{R}^n$(codomain of $\bm{S}$)};
      \node at (4,1.0) {$\mathscr{C}(\bm{S})$};
      %\node[bullet,label=below:$f(x)$] at (4,2.5){};

@@

    \end{tikzpicture}
    \newline
  \end{center}
  \caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to the $\mathscr{C}(\bm{S})$ through the mapping $\bm{S}$}
\end{figure}

Definition \ref{def:cohprob} implies the probability measure on $\mathscr{C}(\bm{S})$ is equivalent to the probability measure on $(\mathbb{R}^m, \bm{\mathscr{F}}^m)$. Hence, there is no density anywhere outside the linear subspace spanned by the columns of $\bm{S}$ in $\mathbb{R}^n$. That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\breve{\bm{y}}_{t+h})$ such that $\bm{f}(\breve{\bm{y}}_{t+h})=0$ for all $\breve{\bm{y}}_{t+h} \in \mathscr{N}(\bm{S})$. Following example will help to understand these definitions more clearly.

@@

Consider a simple hierarchy with two bottom level series $A$ and $B$ that add up to the top level series $Tot$. Suppose the forecasts at time $t+h$ of these series are given by $\breve{\bm{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\breve{\bm{y}}_{t+h} \in \mathbb{R}^3$. Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$. This implies, even though  $\breve{\bm{y}}_{t+h}$ is in $\mathbb{R}^3$, the points actually lie in a two dimensional subspace within that $\mathbb{R}^3$ space. This subspace is equivalent to $\mathscr{C}(\bm{S})$ for this simple hierarchy. Therefore, for any $\breve{\bm{y}}_{t+h} \in \mathscr{N}(\bm{S})$ have a zero probability. I.e. $f(\breve{\bm{y}}_{t+h})=0$ for any $\breve{\bm{y}}_{t+h} \in \mathscr{N}(\bm{S})$.

By the definition of coherent forecasts, it is clear that there are only $m$ number of linear independent series in the whole hierarchy. We refer to these as $m$ dimensional \textit{basis set of series} since these series generates a \textit{basis} that spans the $\mathscr{C}(\bm{S})$. Other $n-m$ series of the hierarchy can be linearly determined by these basis set of series. This implies that any coherent density is a degenerate density. In particular, the $m$ number of bottom level series of a given hierarchy can be considered as a basis set of series. Then the set of columns of $\bm{S}$ is a basis that generates through these bottom level series. This basis spans the linear subspace where the degenerate density lives on.

However bottom level series are not the only set of basis series and we can find many other basis set of series which generates basis that spans the same $\mathscr{C}(\bm{S})$ for a given hierarchy. If we go back to the hierarchy in example 1, instead of two bottom level series $(\bm{A,B})$ we can take $(\bm{Tot,A})$ as the basis set of series and the basis that generates through $(\bm{Tot,A})$ will be
$\{
  \begin{pmatrix} 1&0&1 \end{pmatrix}',
  \begin{pmatrix} 0&1&-1 \end{pmatrix}'\}$.
Another possible basis would be the singular value decomposition of $\bm{S}$.

An important thing to notice here is all of these basis spans the same linear subspace equivalent to the $\mathscr{C}(\bm{S})$. Therefore the definition $(3.2)$ is not unique and one can redefine the coherent probabilistic forecasts with respect to any basis. However, we stick to the definition $(3.2)$ and consider the basis defined by the columns of $\bm{S}$ that generates through the bottom levels of the hierarchy in what follows.

It is also worth to mention that the definition $(3.1)$ and $(3.2)$ facilitate extension to the forecast reconciliation which we talk about in the next section. In contrast to our definition, \citet{BenTaieb2017} defines the coherent probabilistic forecasts in terms of convolution. According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is same as the forecast distribution of the corresponding aggregate series.

@@

Previous studies on point forecast literature have shown that the reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods (\cite{Hyndman2011}; \cite{VanErven2015a}; \cite{Wickramasuriya2017}). However, this was not well established in the context of probabilistic forecasts. Nevertheless, there is no proper definition for the probabilistic forecast reconciliation in the published literature. Thus in this section, we focus on defining the probabilistic forecast reconciliation and discuss how that definition can be used in practice.

@@

Initially we redefine point forecast reconciliation using the concepts in linear algebra as a groundwork for the probabilistic forecast reconciliation.

\begin{definition}
Let $\bm{g}:\mathbb{R}^n \rightarrow \mathbb{R}^m $ and $\hat{\bm{y}}_{t+h} \in \mathbb{R}^n$ be any set of incoherent forecasts at time $t+h$. Then $\tilde{\bm{b}}_{t+h}$ is said to be reconciled bottom level forecasts if
\begin{equation}
  \tilde{\bm{b}}_{t+h}=\bm{g}(\hat{\bm{y}}_{t+h}),
\end{equation}
where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\mathbb{R}^m$. The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S}(\tilde{\bm{b}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})$, where $\bm{S}(\tilde{\bm{b}}_{t+h})$ is the image of $\tilde{\bm{b}}_{t+h}$ under $\bm{S}$ on the $\mathscr{C}(\bm{S}) < \mathbb{R}^n$.
\end{definition}

In the following content we explain more on how this definition can be used in practice to reconcile point forecasts in hierarchical time series. Let $\bm{R} \in \mathbb{R}^{n \times (n-m)}$ consists the columns that spans $\mathscr{N}(\bm{S})$ which is orthogonal to $\mathscr{C}(\bm{S})$. $\mathscr{N}(\bm{S})$ is also equivalent to the $\mathscr{C}(\bm{R})$. Note that $\bm{R}$ is also not unique and one example is a matrix whose columns represent the aggregation constraints for the hierarchy. Then for the hierarchy in example 1,
$$
  \bm{S} =
  \begin{pmatrix}
    1& 1 \\ 1 & 0 \\ 0&1
  \end{pmatrix}
  \quad \text{and} \quad
  \bm{R} =
  \begin{pmatrix}
    1 \\ -1 \\ -1
  \end{pmatrix}.
$$
Further let $\{\bm{s}_1,\dots,\bm{s}_m\}$ and $\{\bm{r}_1,\dots,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,\dots,\bm{s}_m, \bm{r}_1,\dots,\bm{r}_{n-m}\}$ is a basis for $\mathbb{R}^n$. Now, using the insights of definition 4.1, we can use the following steps to reconcile the point forecasts.

@@

This step directly follows by the definition for coherent forecasts. That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \mathbb{R}^n$ to the $\mathscr{C}(\bm{S})$ through $\bm{S}$. Thus we have,
\begin{equation}
  \tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \mathscr{C}(\bm{S})<\mathbb{R}^n.
\end{equation}

Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will result optimally reconciled point forecasts of the hierarchy. Notice that, if the mapping $\bm{g}$ in definition 4.1 is considered to be linear we have,
\begin{equation}
  \bm{g}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot.
\end{equation}

In previous studies on hierarchical point forecasting, $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.
In other words, $\bm{g}$ linearly projects incoherent point forecasts onto the $\mathscr{C}(\bm{S})$. Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible. i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$. This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.

>>>>

	Many research applications often involve a large collection of time series some of which are aggregates of others. These are called hierarchical time series. For example, electricity demand of a country can be disaggregated along a geographical hierarchy. One would be interested in forecasting electricity demand of the whole country along with the demand of states, cities, and households. This is referred to as hierarchical forecasting. An important aspect of hierarchical forecasting is to have coherent forecasts across the hierarchy; that is, forecasts at lower levels should add up to their respective upper levels of aggregation.

	There is a rich literature on producing coherent point forecasts in hierarchical time series. The traditional approaches involve bottom-up, top-down and middle-out methods. In the bottom-up approach, forecasts of the lowest level are first generated and they are simply aggregated to forecast upper levels of the hierarchy \citep{Dunn1976}.  
	In contrast, the top-down approach involves forecasting the most aggregated series first and then disaggregating these forecasts down the hierarchy based on the proportions learn from observed data \citep{Gross1990}. 
	Many studies in the literature have broadly discussed the relative advantages and disadvantages of bottom-up and top-down methods and situations in which they would provide reliable forecasts \citep{Schwarzkopf1988,Kahn1998, Lapide1998,Fliedner2001}.
	A compromise between these two approaches is the middle-out method which entails forecasting each series of a selected middle level in the hierarchy and then forecasting upper levels by the bottom-up method and lower levels by the top-down method. It is apparent that, these three approaches use only a part of the information available when producing coherent forecasts. This might result in inaccurate forecasts. For example, if the bottom level series are highly volatile or too noisy and hence challenging to forecast, then the resulting forecasts from bottom-up approach would be inaccurate.

	As an alternative to these conventional methods, \citet{Hyndman2011} propose to utilize the information from all levels of the hierarchy to obtain coherent point forecasts. This is a two stage process. In the first stage, the forecasts of all series are independently obtained by fitting univariate models for individual series in the hierarchy. It is very unlikely that these forecasts are coherent. Thus in the second stage, these forecasts are optimally combined through a regression model to obtain coherent forecasts. This second step is referred to as reconciliation since it uses a set of incoherent forecasts and revise them to make it coherent. Thus it has given arise to the concept of point forecast reconciliation in hierarchical time series. This study was further improved by \citet{Wickramasuriya2017} to obtain optimally reconciled point forecasts by minimizing the mean squared coherent forecast errors.

	It is also important to notice that the traditional bottom-up, top-down and middle-out forecasting methods are not reconciliation methods since they use only a part of the information from the hierarchy to produce coherent forecasts.

	Providing the associated uncertainty around the point forecasts has been of great interest in recent forecasting literature. This is also referred to as probabilistic forecasts \citep{Gneiting2014}. For example, \citet{McSharry2005} produced probabilistic forecasts in application to electricity demand, \citet{BenTaieb2017} in application to smart meter data, \citet{Pinson2009} in application to wind power generation, \citet{Gel2004}, \citet{Gneiting2005a} and \citet{Gneiting2005} in application to prediction of weather quantities.

	Although there is a thorough literature on producing coherent point forecasts of hierarchical time series, a very limited attention has been given in the context of probabilistic forecasts. Recently \citet{BenTaieb2017} proposed an algorithm to produce coherent probabilistic forecasts with the application to UK electricity smart meter data. This is the only study that copes with the probabilistic forecasts in hierarchical time series thus far. In their approach, a sample from the bottom level predictive distribution will be first generated. This sample will be then aggregated to obtain the coherent probabilistic forecasts of the respective upper levels of the hierarchy. Hence this method is a bottom-up based approach. They propose to use MinT approach for the mean reconciliation of the bottom level predictive distribution and a copula based approach to model the dependency structure of the hierarchy, when generating the sample from bottom level probabilistic forecasts.

	Our contribution in this paper is to provide a proper theoretical background for the probabilistic forecasts reconciliation in hierarchical time series. First, we provide an alternative definition for coherency of point forecasts and the reconciliation of a set of incoherent point forecasts by using the concepts on vector spaces and measure theory. Based on these, we provide a rigorous definition for probabilistic forecast reconciliation and how we can reconcile the incoherent forecast densities in practice. Further, due to the aggregation structure of the hierarchy, the probability distribution is degenerate and hence the forecast distribution should also be degenerate. We discuss in detail how this degeneracy will be taken care of in probabilistic forecast reconciliation and also in the evaluation of their predictive performances. In addition to that, we provide theoretical results on probabilistic forecast reconciliation in the Gaussian framework which is followed by a simulation study to show the importance of reconciliation in the probabilistic framework.

	Rest of the paper is structured as follows. We start with introducing the notations in section 2. In section 3 we provide our definitions for coherency which is followed by the definitions for forecast reconciliation in section 4. Section 5 discusses the methods that can be used for evaluation of probabilistic hierarchical forecasts. Section 6 consists the theoretical results followed by the simulation study on probabilistic forecast reconciliation in the Gaussian framework and we enclose with the remarkable conclusions in section 7.

@@

	We first introduce notations which mostly follow \citet{Wickramasuriya2017}. Suppose $\mathbold{y}_t \in \bm{\mathbb{R}}^n$ comprising all observations of the whole hierarchy at time $t$ and $\mathbold{b}_t \in \bm{\mathbb{R}}^m$ comprising only the bottom level observations at  time $t$. Then due to the aggregation nature of the hierarchy we have,

	\begin{equation}
	\mathbold{y}_t = \mathbold{Sb}_t,
	\end{equation}
	where $\mathbold{S}$ is a $n \times m$ constant matrix whose columns span the linear subspace for which all constraints hold.

	\noindent 
	To understand the notations clearly, consider the hierarchy given in Figure 1.
	\begin{figure}[H]
		\begin{center}
			\leaf{AA} \leaf{AB} 
			\branch{2}{A}
			\leaf{BA} \leaf{BB}
			\branch{2}{B}
			\branch{2}{Tot}
			\qobitree
		\end{center}
		\caption{Two level hierarchical diagram}
	\end{figure}
	\noindent
	In any hierarchy, the most aggregated level is termed as level 0, the second most aggregated level is termed as level 1 and so on. This example consists of two levels. At a particular time $t$, let $y_{Tot,t}$ denote the observation at level 0; $y_{A,t}, y_{B,t} $ denote observations at level 1; and $y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}$ denote observations at level 2. Then $\mathbold{y}_t = [y_{Tot,t},y_{A,t}, y_{B,t},y_{C,t},y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, \\$\mathbold{b}_t = [y_{AA,t}, y_{AB,t}, y_{BA,t}, y_{BB,t}]'$, $m=4$, $n=7$, and $$ \mathbold{S} = \begin{pmatrix} 1& 1 &1 &1  \\ 1 &1 & 0 &0 \\   0&0  & 1 & 1 \\ & & I_4 &   \end{pmatrix}, $$ where $I_4$ is a $4$-dimension identity matrix.

@@

	The main purpose of this section is to provide formal definitions for coherent forecasts. We first give an alternative definition for coherent point forecasts using the properties of vector spaces which is then followed by the definition of coherent probabilistic forecasts.

	\begin{definition}[Coherent subspace]
		Let $\bm{\mathbb{C}}^m$ is a $m$-dimensional subspace of $\bm{\mathbb{R}}^n$, $\bm{\mathbb{C}}^m < \bm{\mathbb{R}}^n$. $\bm{\mathbb{C}}^m$ is said to be a coherent space, if it is spanned by the columns of $\bm{S}$. 
	\end{definition}

	It is worth to notice that the coherent space $\bm{\mathbb{C}}^m$ is equivalent to the column space of $\bm{S}$ which we denote by $\mathscr{C}(\bm{S})$. Further the space orthogonal to $\bm{\mathbb{C}}^m$ is denoted by $\bm{\mathbb{N}}^{n-m}$ and it is equivalent to the null space of $\bm{S}$.

	\begin{definition}[Coherent Point Forecasts]\label{def:cohpoint}
		Suppose $\bm{\breve{y}}_{t+h} \in \mathbb{R}^n$ consists point forecasts of each series in the hierarchy at time $t+h$.  $\bm{\breve{y}}_{t+h}$ is said to be \textit{Coherent} if $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{C}}$. 
	\end{definition}

	\begin{definition}[Coherent Probabilistic Forecasts]\label{def:cohprob}
		Let $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m, \nu^m)$ be a probability triple where $\mathscr{F}^m$ is sigma algebra on $\bm{\mathbb{R}}^m$. Then, $(\bm{\mathbb{C}}, \mathscr{F}_{\bm{S}}, \breve{\nu})$ is said to be coherent probability measure space iff, 
		$$\breve{\nu}(\bm{S}(\bm{A})) = \nu^m(\bm{A}) \quad \forall \quad \bm{A} \in \mathscr{F}^m,$$ 
		where $\bm{S}(\bm{A})$ denotes the image of subset $\bm{A}$ under $\bm{S}$. 
	\end{definition}

@@

			\node at (0,5) {$\mathbb{R}^m$(domain of $\bm{S}$)};
			\node at (4,5) {$\mathbb{R}^n$(codomain of $\bm{S}$)};
			\node at (4,1.0) {$\bm{\mathbb{C}}^m$};
			%\node[bullet,label=below:$f(x)$] at (4,2.5){};

@@

			\end{tikzpicture}
			\newline
		\end{center}
		\caption{Any set $\bm{A} \in \mathbb{R}^m$ will be mapped to the $\bm{\mathbb{C}}^m$ through the mapping $\bm{S}$}
	\end{figure}

	Definition (\ref{def:cohprob}) implies the probability measure on $\bm{\mathbb{C}}^m$ is equivalent to the probability measure on $(\bm{\mathbb{R}}^m, \bm{\mathscr{F}}^m)$. Hence, there is no density anywhere outside the linear subspace $\bm{\mathbb{C}}^m$. That is, a \textit{Coherent probability density forecast} is any density $\bm{f}(\bm{\breve{y}}_{t+h})$ such that $\bm{f}(\bm{\breve{y}}_{t+h})=0$ for all $\bm{\breve{y}}_{t+h} \in \bm{\mathbb{N}}^{n-m}$. Following example will help to understand these definitions more clearly.

@@

	Consider a simple hierarchy with two bottom level series $A$ and $B$ that add up to the top level series $Tot$. Suppose the forecasts at time $t+h$ of these series are given by $\mathbold{\breve{y}}_{t+h} = [\breve{y}_{Tot,t+h},\breve{y}_{A,t+h}, \breve{y}_{B,t+h}]$ and $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{R}}^3$. Due to the aggregation constraint of the hierarchy we have $\breve{y}_{Tot,t+h}=\breve{y}_{A,t+h}+\breve{y}_{B,t+h}$. This implies, even though  $\mathbold{\breve{y}}_{t+h}$ is in $\bm{\mathbb{R}}^3$, the points actually lie in $\bm{\mathbb{C}}^2$, which is a two dimensional subspace within that $\bm{\mathbb{R}}^3$ space. Therefore, for any $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$ have a zero probability. I.e. $f(\mathbold{\breve{y}}_{t+h})=0$ for any $\mathbold{\breve{y}}_{t+h} \in \bm{\mathbb{N}}$.

	For a particular coherent subspace $\bm{\mathbb{C}}^m$, there exist several distinct basis vectors. For example, in the smallest hierarchy considered above, $\left\{\begin{pmatrix} 1&1&0 \end{pmatrix}', \begin{pmatrix} 1&0&1 \end{pmatrix}'\right\}$, $\left\{\begin{pmatrix} 1&0&1 \end{pmatrix}',\\ \begin{pmatrix}
	0&1&-1 \end{pmatrix}'\right\}$ and the singular value decomposition of these two are some alternative basis vectors that spans the same $\bm{\mathbb{C}}^m$. Given a basis for $\bm{\mathbb{C}}^m$, every series of the hierarchy can be linearly determined as a linear combination of that basis vectors. We referred to the coefficients of these linear combinations as the \textit{basis series}. It is apparent that these basis series are $m$ dimensional and linearly independent in a given hierarchy. For example, in the smallest hierarchy, $(\bm{A,B})$ and $(\bm{Tot,A})$ are the basis series corresponds to the basis vectors $\left\{\begin{pmatrix} 1&1&0 \end{pmatrix}', \begin{pmatrix} 1&0&1 \end{pmatrix}'\right\}$ and $\left\{\begin{pmatrix} 1&0&1 \end{pmatrix}', \begin{pmatrix}
	0&1&-1 \end{pmatrix}'\right\}$ respectively. Thus it is clear that the set of bottom level series is a basis series that corresponds to the column vectors of $\bm{S}$.

	An important thing to notice here is, since the basis are not unique for a give coherent subspace, the definition (\ref{def:cohprob}) is not unique and one can redefine the coherent probabilistic forecasts with respect to any basis. However, we stick to the definition (\ref{def:cohprob}) and consider the basis defined by the columns of $\bm{S}$ in what follows.

	It is also worth to mention that the definition (\ref{def:cohpoint}) and (\ref{def:cohprob}) facilitate extension to the forecast reconciliation which we talk about in the next section. In contrast to our definition, \citet{BenTaieb2017} defines the coherent probabilistic forecasts in terms of convolution. According to their definition, if the forecasts are coherent, then the convolution of forecast distributions of disaggregate series is same as the forecast distribution of the corresponding aggregate series.

@@

	Previous studies on point forecast literature have shown that the reconciliation provides better coherent forecasts than the conventional bottom-up and top-down methods (\cite{Hyndman2011}; \cite{VanErven2015a}; \cite{Wickramasuriya2017}). However, not extended in the context of probabilistic forecasts in published literature. Thus our main focus is to rigorously define the probabilistic forecast reconciliation and discuss how that definition can be used in practice.

@@

	Initially we define point forecast reconciliation as a groundwork to the probabilistic forecast reconciliation.

	\begin{definition}\label{def:reconpoint}
		Let $\bm{g}:\bm{\mathbb{R}}^n \rightarrow \bm{\mathbb{R}}^m $ and $\hat{\bm{y}}_{t+h} \in \bm{\mathbb{R}}^n$ be any set of incoherent forecasts at time $t+h$. Then $\tilde{\bm{b}}_{t+h}$ is said to be reconciled bottom level forecasts if 
		\begin{equation}
		\tilde{\bm{b}}_{t+h}=\bm{g}(\hat{\bm{y}}_{t+h}),
		\end{equation}
		where $\bm{g}(\hat{\bm{y}}_{t+h})$ is the image of $\hat{\bm{y}}_{t+h}$ under $\bm{g}$ on $\bm{\mathbb{R}}^m$. The reconciled forecasts for the whole hierarchy is then given by $\tilde{\bm{y}}_{t+h}=\bm{S} \circ \bm{g}(\hat{\bm{y}}_{t+h})$ such that $\tilde{\bm{y}}_{t+h} \in \bm{\mathbb{C}}^m$, where $\bm{S}\circ \bm{g}(.)$ is a projection of $\bm{g}(.)$ onto the $\bm{\mathbb{C}}^m$.
	\end{definition}

	Importance of definition (\ref{def:reconpoint}) is that it facilitates for both linear and non-linear reconciliation. In other words, if $\bm{g}$ is a non-linear function, then the reconciliation of $\hat{\bm{y}}_{t+h}$ will be non-linear. On the other hand, if $\bm{g}$ is a linear function, then $\bm{S}\circ \bm{g}(.)$ will linearly projects incoherent point forecasts onto $\bm{\mathbb{C}}^m$. Latter was the main focus in previous studies in hierarchical point forecasting, where $\bm{g}$ is considered as a $m \times n$ matrix $\bm{P}$ and thus $\tilde{\bm{y}}_{t+h}=\bm{S}\bm{P} \hat{\bm{y}}_{t+h}$.

	In the following content we provide an alternative explanation for linear reconciliation based on definition (\ref{def:reconpoint}). Let $\bm{R} \in \bm{\mathbb{R}}^{n \times (n-m)}$ consists the columns that spans $\bm{\mathbb{N}}^{n-m}$ which is orthogonal to $\bm{\mathbb{C}}^m$. Note that $\bm{R}$ is also not unique and one example is a matrix whose columns represent the aggregation constraints for a given hierarchy. Then for the hierarchy in example 1, 
	$$ 
	\mathbold{S} = 
	\begin{pmatrix} 
	1& 1 \\ 1 & 0 \\ 0&1 
	\end{pmatrix} 
	\quad \text{and} \quad 
	\mathbold{R} = 
	\begin{pmatrix}  
	1 \\ -1 \\ -1 
	\end{pmatrix}.
	$$ 
	\noindent
	Further let $\{\bm{s}_1,...,\bm{s}_m\}$ and $\{\bm{r}_1,...,\bm{r}_{n-m}\}$ denote the columns of $\bm{S}$ and $\bm{R}$ respectively. Then $\bm{B}=\{\bm{s}_1,...,\bm{s}_m, \bm{r}_1,...,\bm{r}_{n-m}\}$ is a basis for $\bm{\mathbb{R}}^n$. Now, using the insights of definition (\ref{def:reconpoint}), we can use the following steps to reconcile the point forecasts.

@@

	This step directly follows by the definition for coherent forecasts. That is, to obtain reconciled point forecasts for the entire hierarchy, we map $\tilde{\bm{b}}_{t+h} \in \bm{\mathbb{R}}^n$ to the $\bm{\mathbb{C}}^m$ through $\bm{S}$. Thus we have, 
	\begin{equation}
	\tilde{\bm{y}}_{t+h}=\bm{S}(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \hat{\bm{y}}_{t+h}, \quad \tilde{\bm{y}}_{t+h} \in \bm{\mathbb{C}}^m<\bm{\mathbb{R}}^n.
	\end{equation}

	Finding a suitable $\bm{R}_\bot$ with respect to a certain loss function will result optimally reconciled point forecasts of the hierarchy. Notice that, if $\bm{P}=(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot$, then the definition for linear reconciliation of point forecasts in previous studies coincides with our explanation.

	Further in our context, we need to find $\bm{R}_\bot$ such that $\bm{R}'_\bot \bm{S}$ is invertible. i.e, $(\bm{R}'_\bot \bm{S})^{-1}\bm{R}'_\bot \bm{S}=\bm{I}$. This condition coincides with the unbiased condition $\bm{SPS}=\bm{S}$ proposed by \citet{Hyndman2011}.
